---
title: "Week11"
author: "Mathi Manavalan"
date: "4/6/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries
```{r message=FALSE}
library(tidyverse)
library(Hmisc)
library(caret)

```

## Data Import and Cleaning

First, I am importing the entire dataset. 
```{r message=FALSE, warning=FALSE}
data <- as_tibble(spss.get("../data/GSS2006.sav", use.value.labels=TRUE)) 


```

Now,we only want the variables relevant to the personality inventory and the respondent's self-reported health. 
For the personality inventory, I am interpreting this to mean the variables (according to the code book for this dataset) from BIG5A1 to BIG5E2 from *The 2006 Module: Personality Traits*. 
For the respondent's self-reported health, I am interpreting this to mean the HEALTH variable.

```{r}
clean <- data %>% 
  select(BIG5A1, BIG5A2, BIG5B1, BIG5B2, BIG5C1, BIG5C2, BIG5D1, BIG5D2, BIG5E1, BIG5E2, HEALTH) %>%
  na.omit() %>% 
  mutate_all(. %>% 
           factor() %>% 
           as.numeric()
         )

```
Responses of 'don't know', 'inapplicable', or other unclearly answered items are appropriately marked as NA according to R, so I removed all rows of data that contain NA (in any column(s)). 

All of the variables are in their appropriate data type (factors), with corresponding levels. I transformed the labeling of all variables to numeric.

## Analysis

Here, I am splitting the clean data into two tibbles. One (holdout) contains a random 250 set from clean, and the other (train) contains the remaining samples from. Then, I am creating an OLS model with 10-fold cross-validation (named olsr).
```{r message=FALSE, include=FALSE}

set.seed(1)

# Shuffle row indices: rows
rows <- sample(nrow(clean))

# Randomly order data
shuffled <- clean[rows, ]

holdout <- clean[1:250, ]

train <- clean[251:nrow(clean), ]

olsr <- train(
  HEALTH ~ .*., 
  holdout,
  method = "lm",
  trControl = trainControl(
    method = "cv", 
    number = 10,
    verboseIter = TRUE
  )
)

```


Here are the output of olsr as well as prediction in holdout.
```{r}
olsr

predict(olsr, holdout)

```

Now I am going to 

*10-fold elastic net regression*
```{r}

```

*support vector regression*
```{r}

```

*extreme gradient boosted regression*
```{r}

```






## Visualization
```{r}

```

